A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-17 article/article.tex
subgraph_isom_histograms
small updates

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_carla_coverage_barchart.png}
    \caption{Coverage barchart for the manually defined coverage scenarios for CARLA.}
    \label{fig:carla_coverage_barchart_manual_scenarios}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_carla.png}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
    \label{fig:carla_coverage_barchart_manual_scenarios}
\end{figure}

@@

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_carla_coverage_barchart.png}
    \caption{Coverage barchart for the manually defined coverage scenarios for CARLA.}
    \label{fig:subgraph_isomorphism_carla_coverage_barchart}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_carla.png}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
    \label{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_carla}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{plots/combined_distributions_plots_speed_distance_carla.png}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
    \label{fig:combined_distributions_plots_speed_distance_carla}
\end{figure}
